taxize - taxonomic search and retrieval in R

### 2013-05-10 inst/doc/taxize_withcode_appA.Rnw
addex appendices environment, small changes to text, added few comments to code

\documentclass[letterpaper,superscriptaddress,showkeys,longbibliography,10pt]{revtex4-1}
\usepackage[utf8]{inputenc}
\usepackage{color,dcolumn,graphicx,hyperref}
\hypersetup
{
colorlinks = true, linkcolor = blue, citecolor = blue, urlcolor = blue,
}

@@

\section{Appendix A. A complete reproducible workflow, from a species list to a phylogeny, and distribution map.}

If you aren't familiar with a complete workflow in R, it may be difficult to visualize the processs. In R, everything is programmatic, so the whole workflow can be in one place, and be repeated whenever necessary. The following is a workflow for taxize, going from a species list to a phylogeny.

@@

Another common task is getting the taxonomic tree upstream from your study taxa. We often know what family or order our taxa are in, but it we often don't know the tribes, subclasses, and superfafamilies. taxize provides many avenues to getting classifications. Two of them are accesible via a single function (\emph{classification}): the Integrated Taxonomic Information System (ITIS) and National Center for Biotechnology Information (NCBI); and via the Catalogue of Life (see function \emph{col\_classification}):

@@

\begin{figure}[!h] 
\centering 
<<phylogeny, eval=TRUE, dev='pdf', out.width='4in', out.height='4in', cache=TRUE, message=FALSE>>=
phylogeny <- phylomatic_tree(taxa=as.character(allnames$spname), taxnames=TRUE, get = 'POST', informat='newick', method = "phylomatic",
    storedtree = "R20120829", taxaformat = "slashpath", outformat = "newick", clean = "true", parallel=TRUE)
phylogeny$tip.label <- capwords(phylogeny$tip.label, onlyfirst=TRUE)
plot(phylogeny)
@
\caption{a phylogeny...} 
\end{figure}

@@

<<installgbif, eval=FALSE>>=
# Install rgbif
install.packages("devtools")
library(devtools)
install_github("rgbif", "ropensci")
@

@@

\begin{figure}[!ht] 
\centering 
<<map, eval=TRUE, dev='pdf', out.width='\\textwidth'>>=
library(rgbif)
library(ggplot2)

occurr_list <- occurrencelist_many(as.character(allnames$spname), coordinatestatus = TRUE, maxresults = 100, removeZeros=TRUE, fixnames="changealltorig")

@@

\end{document}

>>>>

\documentclass[letterpaper,superscriptaddress,showkeys,longbibliography,10pt]{revtex4-1}
\usepackage[utf8]{inputenc}
\usepackage{color,dcolumn,graphicx,hyperref}
\usepackage[titletoc, title]{appendix}
\hypersetup
{
colorlinks = true, linkcolor = blue, citecolor = blue, urlcolor = blue,
}

@@

\begin{appendices}
\section{A complete reproducible workflow, from a species list to a phylogeny, and distribution map.}

If you aren't familiar with a complete workflow in R, it may be difficult to visualize the process. In R, everything is programmatic, so the whole workflow can be in one place, and be repeated whenever necessary. The following is a workflow for taxize, going from a species list to a phylogeny.

@@

Another common task is getting the taxonomic tree upstream from your study taxa. We often know what family or order our taxa are in, but it we often don't know the tribes, subclasses, and superfamilies. taxize provides many avenues to getting classifications. Two of them are accessible via a single function (\emph{classification}): the Integrated Taxonomic Information System (ITIS) and National Center for Biotechnology Information (NCBI); and via the Catalogue of Life (see function \emph{col\_classification}):

@@

\begin{figure}[!h] 
\centering 
<<phylogeny, eval=TRUE, dev='pdf', out.width='4in', out.height='4in', cache=TRUE, message=FALSE>>=
# Fetch phylogeny from phylomatic
phylogeny <- phylomatic_tree(taxa=as.character(allnames$spname), taxnames=TRUE, get = 'POST', informat='newick', method = "phylomatic",
    storedtree = "R20120829", taxaformat = "slashpath", outformat = "newick", clean = "true", parallel=TRUE)
# Format teeth-labels
phylogeny$tip.label <- capwords(phylogeny$tip.label, onlyfirst=TRUE)
# plot phylogeny
plot(phylogeny)
@
\caption{a phylogeny...} 
\end{figure}

@@

<<installgbif, eval=FALSE>>=
# Install rgbif from github.com
install.packages("devtools")
library(devtools)
install_github("rgbif", "ropensci")
@

@@

\begin{figure}[!ht] 
\centering 
<<map, eval=TRUE, dev='pdf', out.width='.8\\textwidth'>>=
library(rgbif)
library(ggplot2)

# get occurences
occurr_list <- occurrencelist_many(as.character(allnames$spname), coordinatestatus = TRUE, maxresults = 100, removeZeros=TRUE, fixnames="changealltorig")

@@

\end{appendices}
\end{document}

### 2013-05-10 inst/doc/taxize_withcode_appA.tex
addex appendices environment, small changes to text, added few comments to code

\usepackage{alltt}
\usepackage[utf8]{inputenc}
\usepackage{color,dcolumn,graphicx,hyperref}
\hypersetup
{
colorlinks = true, linkcolor = blue, citecolor = blue, urlcolor = blue,
}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}

@@

\begin{figure}[!h] 
\centering 
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
phylogeny <- \hlfunctioncall{phylomatic_tree}(taxa = \hlfunctioncall{as.character}(allnames$spname), taxnames = TRUE, 
    get = \hlstring{"POST"}, informat = \hlstring{"newick"}, method = \hlstring{"phylomatic"}, storedtree = \hlstring{"R20120829"}, 
    taxaformat = \hlstring{"slashpath"}, outformat = \hlstring{"newick"}, clean = \hlstring{"true"}, parallel = TRUE)
\end{alltt}
\begin{verbatim}

Retrieving data for species ' Helianthus annuus '

Retrieving data for species ' Pinus contorta '

Retrieving data for species ' Collomia grandiflora '

Retrieving data for species ' Abies magnifica '

Retrieving data for species ' Rosa californica '

Retrieving data for species ' Datura wrightii '

Retrieving data for species ' Mimulus bicolor '

Retrieving data for species ' Nicotiana glauca '

Retrieving data for species ' Madia sativa '

Retrieving data for species ' Bartlettia scaposa '
\end{verbatim}
\begin{alltt}
phylogeny$tip.label <- \hlfunctioncall{capwords}(phylogeny$tip.label, onlyfirst = TRUE)
\hlfunctioncall{plot}(phylogeny)
\end{alltt}
\end{kframe}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcomment{# Install rgbif}
\hlfunctioncall{install.packages}(\hlstring{"devtools"})
\hlfunctioncall{library}(devtools)
\hlfunctioncall{install_github}(\hlstring{"rgbif"}, \hlstring{"ropensci"})
\end{alltt}
\end{kframe}
\end{knitrout}

@@

occurr_list <- \hlfunctioncall{occurrencelist_many}(\hlfunctioncall{as.character}(allnames$spname), coordinatestatus = TRUE, 
    maxresults = 100, removeZeros = TRUE, fixnames = \hlstring{"changealltorig"})

@@

{\centering \includegraphics[width=\textwidth]{figure/map}

>>>>

\usepackage{alltt}
\usepackage[utf8]{inputenc}
\usepackage{color,dcolumn,graphicx,hyperref}
\usepackage[titletoc, title]{appendix}
\hypersetup
{
colorlinks = true, linkcolor = blue, citecolor = blue, urlcolor = blue,
}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}

@@

\begin{figure}[!h] 
\centering 
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcomment{# Fetch phylogeny from phylomatic}
phylogeny <- \hlfunctioncall{phylomatic_tree}(taxa = \hlfunctioncall{as.character}(allnames$spname), taxnames = TRUE, 
    get = \hlstring{"POST"}, informat = \hlstring{"newick"}, method = \hlstring{"phylomatic"}, storedtree = \hlstring{"R20120829"}, 
    taxaformat = \hlstring{"slashpath"}, outformat = \hlstring{"newick"}, clean = \hlstring{"true"}, parallel = TRUE)
\hlcomment{# Format teeth-labels}
phylogeny$tip.label <- \hlfunctioncall{capwords}(phylogeny$tip.label, onlyfirst = TRUE)
\hlcomment{# plot phylogeny}
\hlfunctioncall{plot}(phylogeny)
\end{alltt}
\end{kframe}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcomment{# Install rgbif from github.com}
\hlfunctioncall{install.packages}(\hlstring{"devtools"})
\hlfunctioncall{library}(devtools)
\hlfunctioncall{install_github}(\hlstring{"rgbif"}, \hlstring{"ropensci"})
\end{alltt}
\end{kframe}
\end{knitrout}

@@

\hlcomment{# get occurences}
occurr_list <- \hlfunctioncall{occurrencelist_many}(\hlfunctioncall{as.character}(allnames$spname), coordinatestatus = TRUE, 
    maxresults = 100, removeZeros = TRUE, fixnames = \hlstring{"changealltorig"})

@@

{\centering \includegraphics[width=.8\textwidth]{figure/map}
